---
title: "Slicing & Dicing Mobile Business Performance"
author: "Frank Li"
date: "Monday, November 03, 2014"
output: ioslides_presentation
runtime: shiny

---
```{r,include=FALSE}
library('plyr')
library('ggplot2')
library('scales')
library('ggthemes')
library('dplyr')
source("appVers_GMB_load.R")
source("appVers_GMB_clean.R")
source("appVers_GMB_func.R")
```

## Mobile GMB Share by Platform
```{r,echo=FALSE, warning=FALSE}
renderPlot({
  platGMB_bar
  })
```

## iPhone GMB Share by Version
```{r, echo=FALSE,warning=FALSE}
renderPlot({
  iphoneStack
})
```

## Android GMB Share by Version
```{r, echo=FALSE,warning=FALSE}
renderPlot({
  androidStack
})
```

## iPad GMB Share by Version
```{r, echo=FALSE,warning=FALSE}
renderPlot({
  ipadStack
})
```

## Mobile Web GMB Share by Version
```{r, echo=FALSE,warning=FALSE}
renderPlot({
  mwebStack
})
```

## What will I use this for?
- Eliminate churn from partner questions, enabling self-diagnosis
    - Q: How is iPhone App Version 3.4.2 ramping up? <br /> 
    or <br />
      Q: Which country/platform is tanking overall mobile performance?
    - A: Go look at mobile shiny
- Substance over style
    - Uglier and harder to beautify than Excel, but less manual
    - Tradeoff: <br />
    Learning curve & coding time (higher fixed cost)  <br /> 
    vs.  <br />
    'Cheap' repeatability & fewer q's (lower marginal cost)

## Slide with R Code and Output

```{r}
summary(cars)
```