---
title: "Slicing & Dicing Mobile Business Performance"
author: "Frank Li"
date: "Monday, November 03, 2014"
output: ioslides_presentation
runtime: shiny

---
## Mobile GMB Share by Country
```{r, echo=FALSE}

renderPlot({platGMB_bar})
```

## Mobile GMB Share by App/Version

```{r, echo=FALSE}
inputPanel(
  selectInput("platName", label = "Platform:",
              choices = c('All', 'iPhone', 'Android', 'iPad','Android'), selected = 'All')
  )

renderPlot({
  chartname <- paste0(tolower(platName),'Stack')
  print(get(chartname))
})

#,
#  sliderInput("bw_adjust", label = "Bandwidth adjustment:",
#              min = 0.2, max = 2, value = 1, step = 0.2)
#)

#srenderPlot()

# renderPlot({
#   hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
#        xlab = "Duration (minutes)", main = "Geyser eruption duration")
#   
#   dens <- density(faithful$eruptions, adjust = input$bw_adjust)
#   lines(dens, col = "blue")
#})
```

## What will I use this for?

- Eliminate churn from partner questions, enabling self-diagnosis
    - Q: How is iPhone App Version 3.4.2 ramping up? <br /> 
    or <br />
      Q: Which country/platform is tanking overall mobile performance?
    - A: Go look at mobile shiny
- Substance over style
    - Uglier and harder to beautify than Excel, but less manual
    - Tradeoff: <br />
    Learning curve & coding time (higher fixed cost)  <br /> 
    vs.  <br />
    'Cheap' repeatability & fewer q's (lower marginal cost)

## Slide with R Code and Output

```{r}
summary(cars)
```