---
title: "Analyzing Mobile Business Performance"
author: "Frank Li"
date: "Monday, November 03, 2014"
output: ioslides_presentation
runtime: shiny

---

## Shiny Presentation

This R Markdown presentation is made interactive using Shiny. The viewers of the presentation can change the assumptions underlying what's presented and see the results immediately. 

To learn more, see [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).

## Mobile GMB Share by Country

```{r, echo=FALSE}
inputPanel(
  selectInput("n_breaks", label = "Number of bins:",
              choices = c(10, 20, 35, 50), selected = 20),
  
  sliderInput("bw_adjust", label = "Bandwidth adjustment:",
              min = 0.2, max = 2, value = 1, step = 0.2)
)

renderPlot({
  hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
       xlab = "Duration (minutes)", main = "Geyser eruption duration")
  
  dens <- density(faithful$eruptions, adjust = input$bw_adjust)
  lines(dens, col = "blue")
})
```

## What will I use this for?

- Eliminate churn from partner questions, enabling self-diagnosis
    - Q: How is iPhone App Version 3.4.2 ramping up? <br /> 
    or <br />
      Q: Which country/platform is tanking overall mobile performance?
    - A: Go look at shiny
- Substance over style
    - Uglier and harder to beautify than Excel, but less manual
    - Tradeoff: <br />
    Learning curve & coding time (higher fixed cost)  <br /> 
    vs.  <br />
    'Cheap' repeatability & fewer q's (lower marginal cost)

## Slide with R Code and Output

```{r}
summary(cars)
```